---
title: "Assignment 01"
output: pdf_document
---

```{r, echo=FALSE, results = 'hide', message=FALSE, warning=FALSE}
library(tidyverse)

qrev <- data_frame(
    quarter = 1:4,
    revenue = c(16000, 22000, 26000, 17000)
)
```

This homework will help you to practice and self assess your knowledge and ability around the course concepts.  Use the answer key to assess your work.  


1. Assign a numeric vector with the values $\{1, 4, 12, 7, 2\}$ to an object name `scores`.

2. Assign a character vector with the values $\{CE, Outcomes, Beacon, Engage, Insight\}$ to an object name `product`.

3. Load the **tidyverse** package.

4. Make a 2 column, 4 row, data frame (`data_frame` function) with a column for `quarter` and `revenue`.  Use the values $\{1, 2, 3, 4\}$ for `quarter` and $\{16000, 22000, 26000, 17000\}$ for `revenue`.  Assign the data table to an object named `qrev`.

5. Install and load the **car** package.

6. Use the `?` to view the help file for the `Florida` data set.  What is the cite source for this data set?

7. Use the `View` function to look at the `Florida` data set.  How many people voted for Gore in Flagler County?

8. Load the **carnegie** package.

9. Use the `carnegie` data set and the **ggplot2** package (loaded in **tidyverse** above) to make a bar graph of `BASIC2015` types.

10. Make a scatterplot to examine the relationship between `ROOMS` & `BACCDEG`.  Make sure your plot avoids overplotting issues.

11. Make a histogram to examine the distribution of number of `ROOMS`.  Set the `aes` (`x` position) and `data` globally in the `ggplot` function.  After plotting with the default, adjust the binwidth to an interval of 250 wide.

12. Use **ggplot2** and the `qrev` data set you created above to make this Cleveland dotplot.

```{r, echo = FALSE, fig.width = 3, fig.height = 2.5}
ggplot(data = qrev, aes(x = revenue, y = quarter)) +
    geom_point() 
```