---
title: "Assignment 06"
output: pdf_document
---

This homework will help you to practice and self assess your knowledge and ability around the course concepts.  Use the answer key to assess your work.  

```{r, echo=FALSE, results = 'hide', message=FALSE, warning=FALSE}
library(tidyverse)
library(nycflights13)
```

# Exploratory Data Analysis Recap

Exploratory Data Analysis (EDA) is roughly the following creative process:

1. Generate questions about your data.
1. Search for answers by visualizing & transforming your data.
1. Use what you learn to refine your questions and/or generate new questions.

*For more on EDA see* http://r4ds.had.co.nz/exploratory-data-analysis.html#introduction-3


**You will be sharing the exploration you do in this assignment during next class!**

# Directions

Use EDA to explore one of the following data sets.  Your process will generate many questions.  Use **dplyr** and **ggplot2** to transform and visualize the data in ways that provide insights to the questions.  

```{r, eval = FALSE}
nycflights13::flights
ggplot2::diamonds
exampledata::traffic_violations
exampledata::carnegie
```

# Next Class

For next class be prepared to:

1. Share the data set & initial questions for your EDA.
1. Share and interpret initial tables & visualizations.  Share code as well if you want to.  You can share the tables and plots by using a screen capture them or run the code interactively. Note that there are better ways to save plots and outputs that we'll learn in a few sessions.
1. Share additional questions that the EDA generated.
1. Share and interpret additional tables and visuals that the EDA generated.


